```{r library}
library(tidyverse)
```

```{r visual}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) 
```

```{r facets}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```

# Exercise

1) One column would be made for each unique variable

2) The plots with no points relate to the fact that are no vehicles with those characteristics
``` {r exer}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl)) +
  facet_grid(drv ~ cyl)
```

3) The following code shows the relationship between HWY MPG, drive type, and cylinder count.
``` {r what}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

4) Faceting allows the viewer of the data to separate data points in their mind, so they can look at information individually. However, it is harder to compare data. 
``` {r 4}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

5) Nrow counts the number of rows you want, while Ncol does this for columns. Facet grind is set in these fields. 

6) In facet grind the more unique variables should be put in the columns because it is more legible
