---
title: "Visualizing Starwars characters"
author: "Julian Siegel"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
```

1.  Glimpse at the starwars data frame.

```{r}
#| label: glimpse-starwars

glimpse(starwars)
```

2.  Modify the following plot to change the color of all points to `"pink"`.

```{r}
#| label: scatterplot

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "pink")
```

3.  Add labels for title, x and y axes, and size of points. Uncomment to see the effect.

```{r}
#| label: scatterplot-labels

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "#30509C") +
  labs(
    #title = "Height, Mass, and Birth Year of Star Wars Characters",
    #x = "Height", 
    #y = "Mass",
    # Birth Year
    )
```

4.  Pick a single numerical variable and make a histogram of it. Select a reasonable binwidth for it.

(A little bit of starter code is provided below, and the code chunk is set to not be evaluated with `eval: false` because the current code in there is not valid code and hence the document wouldn't knit. Once you replace the code with valid code, set the chunk option to `eval: true`, or remove the `eval` option altogether since it's set to `true` by default.)

```{r}
#| label: histogram
#| eval: true

ggplot(starwars, aes(x = birth_year)) +
#  geom_histogram( stat = "bin", binwidth = 7.5)
    geom_histogram(binwidth = 10)
```

5.  Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) to visualization the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: num-cat
ggplot(starwars, aes(x = gender, y = height, color = homeworld) ) +
  geom_point()

```

In this graph, I wanted to look at the relationship between height, gender, and the homeworld of the characters. Through this I wanted to see whether any homeworlds were dominated by specific heights or genders. 

6.  Pick a single categorical variable from the data set and make a bar plot of its distribution.

```{r}
#| label: barplot
ggplot(starwars, aes(x = homeworld))+
  geom_bar()
```
I wish I was able to have the homeworld names written in a more clear way so that I could see what specific worlds dominated here. 

7.  Pick two categorical variables and make a visualization to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: cat-cat
ggplot(starwars, aes(x = height, y = species, color = sex)) +
  geom_point()

```

I wanted to analyze the height variations between species. I decided to add sex as well, because I was interested in what that breakdown was in the data as well. 

8.  Pick two numerical variables and two categorical variables and make a visualization that incorporates all of them and provide an interpretation with your answer.

(This time no starter code is provided, you're on your own!)

```{r}
#| label: multi
ggplot(starwars, aes(x = hair_color, y = eye_color, color = birth_year, size = mass )) +
  geom_point()
```

I wasn't really sure what data to use on this one. I do find it cool that birth year was made into a color slider. 